### 2016-03-12 paper/stereo.tex
Hang

Since the optimization in the above stereo problem is fairly easy, we
compare our method with both parallel alpha expansion
\cite{first_fusion_viktor} and hierarchy fusion \cite{olga}.

add Alpha Expansion.
uniform and random splitting for parallel alpha expansion

>>>>

Since the optimization in the above stereo problem is fairly easy, we
compare our method with standard sequential alpha expansion, parallel
alpha expansion \cite{first_fusion_viktor} and hierarchy fusion
\cite{olga}. In all experiment, we use $\alpha$-expansion to fuse
single label proposals, and QPBO to fuse multi-label proposals.
